### 2018-05-05 papers/synth/experiments.tex
some cleanup

\begin{table}[t]
  \centering
  \begin{tabular}[t]{|c|c|c|c|c|c|c|c|c|c|c}\hline
    {\multirow{2}{*} \textbf{Size}}  & \multicolumn{2}{c|}{\textbf{Add edge}} & \multicolumn{2}{c|}{\textbf{Add molecules}} & \multicolumn{2}{c|}{\textbf{Low depth Cnf}}  &  \multicolumn{2}{c|}{\textbf{Gate function}} &  \multicolumn{2}{c|}{\textbf{VTS repair}} \\\hline

@@

We implemented the encodings in a tool called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in its custom designed
input language. The input is then converted to the constraints over VTS. 
%
The tool can not only synthesize the above discussed query, but also their
combination.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
processing formulas. 
%
Since, the formulas involve alternation of quantifiers over Boolean variables Z3 is not a suitable choice. We translate the formula created by Z3 tool into standard QDIMACS~\cite{qdimacs} format. Which can be used as an input for most of the QBF solvers.

%Since the formulas are in QBF, we cannot use~\zthree.
%
We use~\depqbf~\cite{lonsing2010depqbf} for solving of QBF formulas. 
%
Our tool includes about 7000 lines of code.

We have applied~\ourtool~on six partially defined VTS.
%
The results are presented in table~\ref{tab:qf-graph}.
%
The experiments were conducted on ... machine,
with \ashu{?}GB memory and 900s timeout.
%
The first four VTSs are synthetic and inspire from literature for typical
motifs in VTSs. 
%
%
The fifth VTS is taken from "A complete set of SNAREs in yeast"
~\cite{burri2004complete} paper. It has been adapted from the paper by separating the v and the t SNAREs. 
%The t SNAREs are labelled within compartments and v SNAREs on the edges. %\ashu{Describe the source of two examples}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.

@@

Variation 1 of our tool adds new labelled edges to the graph. We have ranked the all possible graph edits with the simple rank of minimum updates. Our tools were able to complete this graph by adding five new edges and nine new molecules in 210s. Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s. Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s. Variation 4 of our tool synthesis Boolean function based on AND, OR gates. The result shows the basic template of 4 leaves and 3 gates we allow the user to provide its own template in our front-end language. The tool was able to synthesize the Boolean functions in 470s.
%
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%

>>>>

\begin{table}[t]
  \centering
  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}}\hline
    {\multirow{2}{*} \textbf{Size}}  & \multicolumn{2}{c|}{\textbf{Add edge}} & \multicolumn{2}{c|}{\textbf{Add molecules}} & \multicolumn{2}{c|}{\textbf{Low depth Cnf}}  &  \multicolumn{2}{c|}{\textbf{Gate function}} &  \multicolumn{2}{c|}{\textbf{VTS repair}} \\\hline

@@

We implemented the encodings in a tool
called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS. 
%
The tool can not only synthesize the above discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
Our tool is developed in C++ and uses~\zthree~\cite{z3} infrastructure for
processing formulas. 
%
Since, the formulas involve alternation of quantifiers over Boolean
variables Z3 is not a suitable choice.
%
We translate the formula created by Z3 tool into standard
QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
%
We use~\depqbf~\cite{lonsing2010depqbf} for solving of QBF formulas. 
%
Our tool includes about 7000 lines of code.

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in table~\ref{tab:qf-graph}.
%
The experiments were conducted on ?? machine,
with \ashu{?}GB memory and 900s timeout.
%
The first four VTSs are synthetic, but inspire from literature for
typical motifs in VTSs. 
%
%
The fifth VTS is taken from "A complete set of SNAREs in yeast"
~\cite{burri2004complete} paper. It has been adapted from the paper by
separating the v and the t SNAREs. 
%The t SNAREs are labelled within compartments and v SNAREs on the edges. %\ashu{Describe the source of two examples}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.

@@

Variation 1 of our tool adds new labelled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
%
Our tools were able to complete this graph by adding five new edges
and nine new molecules in 210s.
%
Variation 2 of our graph adds new labels to the edge and was able to
fix this graph with eleven new molecule labels in 180s.
%
Variation 3 of our tool synthesis low depth CNF functions and was able
to synthesis the result in 500s.
%
Variation 4 of our tool synthesis Boolean function based on AND, OR
gates.
%
The result shows the basic template of 4 leaves and 3 gates we allow
the user to provide its own template in our front-end language.
%
The tool was able to synthesize the Boolean functions in 470s.
%
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%

### 2018-05-05 papers/synth/intro.tex
some cleanup

We use the model of VTSs that has been presented in~\cite{VTS}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.
% Describe VTS in detail

@@

We have implemented the encoding in a flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on two found-in-nature VTSs, namely
M1~\cite{} and S1~\cite{burri2004complete}.
%
We have also applied our tool on various synthetic examples to
demonstrate that our tool scale upto the graph size size nodes, which
is the size of typical VTSs in a eukaryotic cell.

>>>>

We use the model of VTSs that has been presented in~\cite{shukla2017discovering}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.
% Describe VTS in detail

@@

We have implemented the encoding in a flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on two found-in-nature
VTSs~\cite{burri2004complete}.
%
We have also applied our tool on various synthetic examples to
demonstrate that our tool scale upto the graph size size nodes, which
is the size of typical VTSs in a eukaryotic cell.

### 2018-05-05 papers/synth/prelim.tex
caps
some cleanup

In this section, we will present the model of VTS from~\cite{PloS,SASB}.
%
We will also present the constrains and properties on the VTSs, and their
encoding as a QBF formula.   
%
We model a VTS as labelled graph along with assisting pairing matrices and
activating functions.

@@

\item Boolean variable $n_{i,m}$ indicates if $m \in \nlabel(i)$
\item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
\item Boolean variable $p_{m_1,m_2,m_3,m_4}$ indicates if $\{m_1,m_2,m_3,m_4\} \in \pairs$
\item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
encoding $\nodef(m)$ map
\item uninterpreted Boolean functions $\edgef_m : \booleans^\mu \maps \booleans$
encoding $\edgef(m)$ map
\end{enumerate}
We also have auxiliary Boolean variables that will help us encode the well-fused property. 
\begin{enumerate}
\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
  holds
\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
\end{enumerate}

@@

The following constraints encode the basic consistency of VTSs.
\begin{align*}
  \texttt{EdgeC} =\;& \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
  \land
  \bigwedge\limits_{i,q} \neg e_{i,i,q}
  \land
  % \tag{\texttt{NodeC}}\label{eq:f0}\\
  \bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
  \\
  \texttt{ActivityC} =\;&
  \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
  % \tag{V2}\label{eq:f1}\\
  \\
  \texttt{PairingC} =\;&
  \exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
                         (p_{m_1,m_2,m_3,m_4} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) \land\\ 
  & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
  % \bigwedge\limits_{m} 
  % (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
  % (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
  \\
  \texttt{Fusion1} =\;&
  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
  \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
                        \sum_{l=1}^4 b_{i,j,q,m_l} > 0 \land\\
  & \qquad \qquad \qquad \qquad \sum_{l=1}^4 a_{j,m_l} > 0 \land p_{m_1,m_2,m_3,m_4})
  \\
  \texttt{Fusion2} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \neg 
  \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4})
  \\
  \texttt{Consistancy} =\;& \texttt{EdgeC} \land
  \texttt{ActivityC} \land \texttt{PairingC} \land
  \texttt{Fusion1} \land \texttt{Fusion2} 
\end{align*}
\texttt{EdgeC} states that each edge has at least one molecule,
there are no self loops, and edge labels are consistent with node labels.   
\texttt{ActivityC} states that active molecule are present.
\texttt{PairingC} states that a molecule can either participate in fusion
via nodes or via edges, but not both.
\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
\texttt{Consistancy} is the conjunction of all of the above.

@@

For synthesis of incomplete systems,
we need properties  against which we synthesize the missing parts.
%
Here we will discussed two such properties proposed in earlier
works~\cite{SASBpaper}, namely stability and $k$-connectedness.
%

>>>>

In this section, we will present the model of VTS from~\cite{smtVTS}.
%
We will also present the constrains and properties on the VTSs, and their
encoding as a QBF formula.   
%
We model a VTS as labelled graph along with assisting pairing matrices and
activating functions.

@@

\item Boolean variable $n_{i,m}$ indicates if $m \in \nlabel(i)$
\item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
\item Boolean variable $p_{\{m_1,m_2,m_3,m_4\}}$ indicates if $\{m_1,m_2,m_3,m_4\} \in \pairs$
\item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
encoding $\nodef(m)$ map
\item uninterpreted Boolean functions $\edgef_m : \booleans^\mu \maps \booleans$
encoding $\edgef(m)$ map
\end{enumerate}
We also have auxiliary Boolean variables that will help us encode the well-fused property. 
\begin{enumerate}
\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
  holds
\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
\end{enumerate}

@@

The following constraints encode the basic consistency of VTSs.
\begin{align*}
  \texttt{EdgeC} =\;& \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
  \land
  \bigwedge\limits_{i,q} \neg e_{i,i,q}
  \land
  % \tag{\texttt{NodeC}}\label{eq:f0}\\
  \bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
  \\
  \texttt{ActivityC} =\;&
  \bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
  % \tag{V2}\label{eq:f1}\\
  \\
  \texttt{PairingC} =\;&
  \exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
                         (p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
% \land\\ 
%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
  % \bigwedge\limits_{m} 
  % (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
  % (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
  \\
  \texttt{Fusion1} =\;&
  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
  \bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
                        \Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
  & \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
  \\
  \texttt{Fusion2} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \neg 
  \bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
  \\
  \texttt{Consistancy} =\;& \texttt{EdgeC} \land
  \texttt{ActivityC} \land \texttt{PairingC} \land
  \texttt{Fusion1} \land \texttt{Fusion2} 
\end{align*}
\texttt{EdgeC} states that each edge has at least one molecule,
there are no self loops, and edge labels are consistent with node labels.   
\texttt{ActivityC} states that active molecule are present.
\texttt{PairingC} states that a molecule can either participate in fusion
via nodes or via edges, but not both.
\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
\texttt{Consistancy} is the conjunction of all of the above.

@@

For synthesis of incomplete systems,
we need properties  against which we synthesize the missing parts.
%
Here we will discussed two such properties proposed in earlier
works~\cite{smtVTS}, namely stability and $k$-connectedness.
%
